Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Fix grammar, clarify with concision.

The current Raft.js implementation most of the Raft algorithm
including: leader election, log replication, safety, membership
changes, basic client interaction, and read-only operation
optimizations. % TODO: read-only operations needs mentioning earlier
Log compaction and full client linearizability are not currently
implemented (clients and client transactions are not assigned unique
IDs). Log compaction is important for long-running production systems
in order to limit memory growth and allow new nodes to catch up their
logs more efficiently. However log compaction is not required for
verifying overall system correctness and does not significantly impact
short-running test configurations. Full client linearizability is
important feature for simplifying certain types of distributed
applications, however the implementation of linearizability requires
some significant additions to the Raft implementation (e.g. assigning
client IDs and sequence IDs and tracking timed-out clients). For the
chat application, simply adding a single atomic check-and-set state
machine command is sufficient to achieve a linearized chat history.
This does impose a slight additional cost on the client because it
must retry the atomic operations until they succeed. The author
intends to implement both log compaction and full client
linearizability in the future, however these do not have a significant
impact on the ability to test Raft combined with WebRTC.

>>>>

The current version of Raft.js implements most of the Raft algorithm
including: leader election, log replication, safety, membership
changes, basic client interaction, and read-only operation
optimizations. % TODO: read-only operations needs mentioning earlier
Log compaction and full client linearizability are not currently
implemented (clients and client transactions are not assigned unique
IDs). Log compaction is important for long-running production systems
in order to limit memory growth and allow new nodes to catch up their
logs more efficiently. However log compaction is not required for
verifying overall system correctness and does not significantly impact
short-running test configurations. Full client linearizability is
important feature for simplifying certain types of distributed
applications, however the implementation of linearizability requires
some significant additions to the Raft implementation (e.g. assigning
client IDs and sequence IDs and tracking timed-out clients). For the
chat application, simply adding a single atomic check-and-set state
machine command is sufficient to achieve a linearized chat history.
This does impose a slight additional cost on the client because it
must retry the atomic operations until they succeed. The author
intends to implement both log compaction and full client
linearizability in the future, however these do not have a significant
impact on the ability to test Raft combined with WebRTC.
